Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-09-08 review/response.Rmd

-   "Sometimes, two optimisers can start with the same basis but finish with bases of opposite sign...However, this creates difficulties for comparing the optimisers since the end bases will be symmetric to the origin. A sign flipping step is conducted..." and the "Reconciling the orientation" section

    -   For 1D projections, flipping the sign is sufficient. For p-D projections of $\mathbb{R}^n$​, one may need a little more. To my knowledge most index functions are invariant to any rotations that happens within the p-subspace. This makes me wonder that in general, one may want to align two bases so that their difference does not contain any "within-subspace" components. In other words, one may want to compare representations in the Grassmannian manifold (space of k-subspaces) instead of in the Stiefel manifold (space of orthonormal k-frames).

\textcolor{red}{With p-D bases, the correction of orientation is a bit more complicated since both rotation and flip need to be taken into account. For 2D bases, one need to check if the two frames are spanning the same subspace and pointing at the same direction.}

\textcolor{magenta}{We agree that most index functions should be rotation invariant (this is in fact a desirable property, but there are exceptions where indexes can still be very useful but not rotation invariant, see discussion in Laa, Cook (2020)). Thus when comparing frames defining projections to d>=2 dimensions, we may want to introduce a rotation that will align the bases as much as possible within the common subspace, while potentially quantifying e.g. the angle between two planes. This is an interesting problem, however the implementation of this general approach is beyond the scope of the current paper. XXX do you want to mention something about this in the paper?}

### 2021-09-08 paper/zhang-cook-laa-langrene-menendez.Rmd
Small changes to conclusions and reply

Experiments in this paper have shown that random search algorithms tend to require larger search size for 2D indexes as compared to 1D indexes. All the three optimisers tend to work well for smooth indexes while PD generally fails for non-smooth indexes. This is due to the fact that derivative based methods are in general not suitable for optimising non-smooth functions.

For other researchers, the tools implemented in the ferrn package can track the progression of the target function and monitor parameter coverage of the search space in both reduced 2D space and the full space. These visualisation can lead to insights for evaluating the performance of multiple optimisers in a specific problem, as the example shown for comparing the three optimisers when optimising the kolmogorov index in the paper.

>>>>

The tools were implemented in the ferrn package and can track the progression of the target function and monitor parameter coverage of the search space in both reduced 2D space and the full space. These visualisation can lead to insights for evaluating and comparing the performance of multiple optimisers in a specific problem. They can provide better understanding of existing methods or motivate the development of new approaches. For example, we have compared how three optimisers perform when maximising a non-smooth index function and illustrated how the pseudo-derivative search fails in this setting. The observations from our experiments have also been translated into improved optimisation methods for the guided tour, e.g. we introduced the option to interrupt the search if a better basis is found along the path.
